%-------------------------
% Resume in Latex
% Author : Dilan David
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://DatscIY.com/}{\Large Dilan David}} & Email : \href{mailto:dilan.david@gmail.com}{dilan.david@gmail.com}\\
  \href{http://DatscIy.com/}{http://www.DatscIY.com} & Mobile : +1-614-546-8484 \\
\end{tabular*}

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, SQL, NoSQL, VBA, HTML, CSS}
      \hfill
      \textbf{Databases}{: Relational and Unstructured: AWS, BigQuery, Azure, MongoDB}\\
    }
    \item{
      \textbf{Software}{: Tableau, Excel, IBM Cognos/Watson, Zarca, Fieldglass, SAP Ariba}\\
    }
    \item{
      \textbf{Hard Skills}{: Data Pre-Processing, Quantitative Analysis, Data Visualization, Predictive Modeling, Natural Language Processing, Machine Learning}
    }
    \item{
      \textbf{Soft Skills}{: Written and Verbal Communication, Collaration, Project Management, Presentation, Design Thinking, Accessibility}
    }
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Nationwide Insurance}{Columbus, OH}
      {Specialist, Risk \& Analytics}{Apr 2018 - Present}
      \resumeItemListStart
        \resumeItem{KPI Dashbaords}
          {Developed and implemented KPIs to manage vendor SLAs.}
        \resumeItem{Automation}
          {Created macros and formulas to streamline monthly reporting and improve delivery times.}
        \resumeItem{Savings}
          {Helped recoup over \$5M ($\approx$\$1.5M annually) in discounts and rebates based on contractual terms.}        
        \resumeItem{Continuous Improvement}
          {Worked on continuous improvement initiatives to streamline reporting access.}
          \resumeItemListEnd
    \resumeSubSubheading
      {Specialist, Supplier Relationship Management}{Feb 2016 - Apr 2018}
      \resumeItemListStart
        \resumeItem{Survey Analysis}
          {Designed and executed surveys and provided quantitative analytics on the results.}
        \resumeItem{Administration}
          {Assisted with software integration, maintenance and managed user access.}
        \resumeItemListEnd
   
    \resumeSubheading
      {Garden City Group}{Dublin, OH}
      {Project Administrator}{Sep 2011 - Feb 2016}
      \resumeItemListStart
        \resumeItem{ETL Lifecycle}
          {Extracted and pre-processed Client data for load.}
        \resumeItem{Savings}
          {Performed cost-benefit analysis to avoid pre-payment penalties in bankruptcy settlements.}
        \resumeItem{Oversight}
          {Ensured that settlement disbursements were calculated accurately based on the Court approved Plan of Allocation.}
        \resumeItem{KPI Dashboards}
          {Developed and administered weekly operation metrics to monitor Team's workload and efficiency.}
        \resumeItem{Communication}
          {Received and handled Client inquiries via phone and email.}
        \resumeItemListEnd
    \resumeSubSubheading
      {Research Associate}{2010-2011}
      \resumeItemListStart
        \resumeItem{Research}
          {Researched potential fraudulent securities claims to be submitted to the DOJ for review.}
      \resumeItemListEnd

    \resumeSubheading
      {JP Morgan Chase}{Columbus, OH}
      {Customer Care Professional}{Jan 2009 - Nov 2009}
      \resumeItemListStart
        \resumeItem{Financial Analysis}
          {Reviewed and analyzed customer financial data and provided recommendations for loan modifications.}
        \resumeItem{Communication}
          {Received and handled inbound calls and emails from Clients.}
        \resumeItem{Sales}
          {Increased credit card, home equity and refinance sales by offering Chase products to existing and new customers.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Relevant Coursework}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bowling Green State University}{Ohio}
      {Calculus I \& II}{Aug 2004 - Jun 2006}
    \resumeSubheading
      {Columbus State Community College}{Ohio}
      {Calculus Statistics and Algebra}{Aug 2006 - Jun 2007}
    \resumeSubheading
      {EdX}{MOOC}
      {Essential Statistics for Data Analysis}{Jun 2017}
    \resumeSubheading
    {UCSanDiegoX}{MOOC}
    {Python for Data Science}{Dec 2018}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source python library for financial data analysis and machine learning for finance.}
%     \resumeSubItem{Github Visualization}
%       {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%     \resumeSubItem{Recommendation System}
%       {Music and Movie recommender systems using collaborative filtering on public datasets.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%   \resumeSubHeadingListEnd

%-------------------------------------------

\end{document}
